Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-27 awipev-CO2.Rmd
removed pH and pCO2 calculated in situ which are meaningless (at and ct sampled in the FB)

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
#discrete_is_na$pco2_calc<- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

# pH calculated (at and ct) at in situ (11 m) sal and temp
discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_mix)  & !is.na(temp_insitu_11m) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_mix)  | is.na(temp_insitu_11m) | is.na(at) | is.na(ct))
carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_mix, T = discrete_no_na$temp_insitu_11m, P = 11/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
discrete_no_na$phcalc_insitu <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
discrete_no_na$pco2_calc_insitu <- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_insitu <- NA
discrete_is_na$pco2_calc_insitu <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

@@

# pH calculated in situ
discrete2merge <- discrete %>%
  dplyr::select(closest_datetime, phcalc_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

>>>>

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
#discrete_is_na$pco2_calc<- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```

@@
